Optimal (Multiway) Spatial Joins

### 2024-09-19 msj.tex
yufei

%\documentclass[sigconf]{acmart}
\documentclass[acmsmall,review,anonymous]{acmart}
% \documentclass{...}
%\input{./def/yf-formatting}
\input{./def/yf-def}

@@

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-4mm}}

@@

%====== from acm ======
\acmDOI{}
\acmISBN{}

\acmConference[]{...}{...}{...}
\acmYear{...}
\copyrightyear{}
\acmArticle{}
\acmPrice{}
%======================

@@

\title{Optimal (Multiway) Spatial Joins}

% \author{}
% \affiliation{
% 	\institution{Chinese University of Hong Kong}
% 	\city{Hong Kong}
% 	\country{China}}

\author{}

@@

@@

\begin{figure*}
    \begin{tabular}{cc}
        \includegraphics[height=30mm]{./artwork/prob-a} &
        \includegraphics[height=27mm]{./artwork/prob-b}  \\[2mm]
        (a) Problem $\mathscr{A}$ &
        \hspace{3mm}
        (b) Problem $\mathscr{B}$ \\[3mm]
    \end{tabular}
    %\vspace{3mm}
    \begin{tabular}{ccc}
        \includegraphics[height=30mm]{./artwork/prob-c} &
        \includegraphics[height=30mm]{./artwork/prob-d} &
        \includegraphics[height=30mm]{./artwork/prob-e} \\[2mm]
        (c) Problem $\mathscr{C}$ &
        (d) Problem $\mathscr{D}$ &
        (e) Problem $\mathscr{E}$
    \end{tabular}

    \figcapup
    \caption{Four geometric building brick problems}
    \label{fig:probs}
    \figcapdown
\end{figure*}

@@

As mentioned before, for a result tuple $(r_1, ..., r_{k-2}, h, v)$ of this type, a rectangle $r_i$, for some $i \in [k-2]$, covers an endpoint of $h$ or $v$ or both. As (i) there are $k-2$ choices for $i$ and (ii) $h$ and $v$ together have four endpoints, we can divide Type 2 further into $4(k-2)$ ``sub-types'': in subtype 1 (resp., 2), $r_1$ covers the left (resp., right) endpoint of $h$, in subtype 3 (resp., 4), $r_1$ covers the bottom (resp., top) endpoint of $v$, in subtype 5 (resp., 6), $r_2$ covers the left (resp., right) endpoint of $h$, etc. It is possible for the result tuple to belong to multiple sub-types simultaneously. Next, we will focus on producing the result tuples of a particular sub-type:
\myeqn{
    \J_2  &=& \{(r_1, ..., r_{k-2}, h, v) \in \J(R1, ..., R_{k-2}, H, V) \mid \text{$r_{k-2}$ covers the left endpoint of $h$}\}. \label{eqn:hv:type2:J2}
}
The other sub-types can be found analogously.

@@

\balance

>>>>

%\documentclass[sigconf]{acmart}
%\documentclass[acmsmall,review,anonymous]{acmart}
\documentclass[acmsmall]{acmart}
% \documentclass{...}
%\input{./def/yf-formatting}
\input{./def/yf-def}

@@

\def\vgap{\vspace{0mm}}
\def\extraspacing{\vspace{1mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-4mm}}

@@

%====== from acm ======
\setcopyright{acmlicensed}
\acmJournal{PACMMOD}
\acmYear{2024} \acmVolume{2} \acmNumber{5 (PODS)} \acmArticle{210} \acmMonth{11}\acmDOI{10.1145/3695828}

\received{May 2024}
\received[accepted]{August 2024}

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10003752.10003809</concept_id>
       <concept_desc>Theory of computation~Design and analysis of algorithms</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Design and analysis of algorithms}
%======================

@@

\title{Optimal (Multiway) Spatial Joins}
\titlenote{This work was supported in part by GRF projects 14207820, 14203421, and 14222822 from HKRGC.}

\author{Ru Wang}
\email{rwang21@cse.cuhk.edu.hk}
\author{Yufei Tao}
\email{taoyf@cse.cuhk.edu.hk}
\affiliation{%
  \institution{The Chinese University of Hong Kong}
  \city{Hong Kong}
  \state{Shatin}
  \country{China}
}

@@

% \begin{acks}
%     This work was supported in part by GRF projects 14207820, 14203421, and 14222822 from HKRGC.
% \end{acks}

@@

% \begin{figure*}
%     \begin{tabular}{cc}
%         \includegraphics[height=30mm]{./artwork/prob-a} &
%         \includegraphics[height=27mm]{./artwork/prob-b}  \\[2mm]
%         (a) Problem $\mathscr{A}$ &
%         \hspace{3mm}
%         (b) Problem $\mathscr{B}$ \\[3mm]
%     \end{tabular}
%     %\vspace{3mm}
%     \begin{tabular}{ccc}
%         \includegraphics[height=30mm]{./artwork/prob-c} &
%         \includegraphics[height=30mm]{./artwork/prob-d} &
%         \includegraphics[height=30mm]{./artwork/prob-e} \\[2mm]
%         (c) Problem $\mathscr{C}$ &
%         (d) Problem $\mathscr{D}$ &
%         (e) Problem $\mathscr{E}$
%     \end{tabular}
%
%     \figcapup
%     \caption{Four geometric building brick problems}
%     \label{fig:probs}
%     \figcapdown
% \end{figure*}

\begin{figure*}
    \begin{tabular}{ccccc}
        \includegraphics[height=23mm]{./artwork/prob-a} &
        \includegraphics[height=23mm]{./artwork/prob-b} &
        \includegraphics[height=23mm]{./artwork/prob-c} &
        \includegraphics[height=23mm]{./artwork/prob-d} &
        \includegraphics[height=25mm]{./artwork/prob-e} \\[2mm]
        (a) Problem $\mathscr{A}$ &
        (b) Problem $\mathscr{B}$ &
        (c) Problem $\mathscr{C}$ &
        (d) Problem $\mathscr{D}$ &
        (e) Problem $\mathscr{E}$
    \end{tabular}
    \figcapup
    \caption{Five geometric building brick problems}
    \label{fig:probs}
    \figcapdown
\end{figure*}

@@

As mentioned before, for a result tuple $(r_1, ..., r_{k-2}, h, v)$ of this type, a rectangle $r_i$, for some $i \in [k-2]$, covers an endpoint of $h$ or $v$ or both. As (i) there are $k-2$ choices for $i$ and (ii) $h$ and $v$ together have four endpoints, we can divide Type 2 further into $4(k-2)$ ``sub-types'': in subtype 1 (resp., 2), $r_1$ covers the left (resp., right) endpoint of $h$, in subtype 3 (resp., 4), $r_1$ covers the bottom (resp., top) endpoint of $v$, in subtype 5 (resp., 6), $r_2$ covers the left (resp., right) endpoint of $h$, etc. It is possible for the result tuple to belong to multiple sub-types simultaneously. Next, we will focus on producing the result tuples of a particular sub-type:
\myeqn{
    \J_2  &=& \{(r_1, ..., r_{k-2}, h, v) \in \J(R_1, ..., R_{k-2}, H, V) \mid \text{$r_{k-2}$ covers the left endpoint of $h$}\}. \label{eqn:hv:type2:J2}
}
The other sub-types can be found analogously.

@@
